---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/cruxjars.svg?branch=master)](https://travis-ci.org/hrbrmstr/cruxjars) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/cruxjars/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/cruxjars)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/cruxjars)](https://cran.r-project.org/package=cruxjars)

# cruxjars

Java Archive Wrapper Supporting the 'crux' Package

## Description

Contents of the 'crux' & supporting Java archives 
<https://github.com/chimbori/crux>.Version number reflects the version 
number of the included 'JAR' file.

## Installation

```{r install-ex, eval=FALSE}
install.packages(c("cruxjars", "crux"), repos = "https://cinc.rud.is/")
```

## Usage

```{r lib-ex}
library(cruxjars)
library(crux)

# current version
packageVersion("crux")

```

```{r}
str(
  summarise_url("http://time.com/5541738/joe-biden-backtracks-pence-praise-criticism/"), 1
)
```

```{r}
str(
  classify_url("https://www.washingtonpost.com/powerpost/house-democrats-explode-in-recriminations-as-liberals-lash-out-at-moderates/2019/02/28/c3d163fe-3b87-11e9-a06c-3ec8ed509d15_story.html")
)
```

## crux Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
