---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/cruxjars.svg?branch=master)](https://travis-ci.org/hrbrmstr/cruxjars) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/cruxjars/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/cruxjars)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/cruxjars)](https://cran.r-project.org/package=cruxjars)

# cruxjars

Java Archive Wrapper Supporting the 'crux' Package

## Description

Contents of the 'crux' & supporting Java archives 
<https://github.com/chimbori/crux>.Version number reflects the version 
number of the included 'JAR' file.

## What's Inside The Tin

The following functions are implemented:

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://sr.ht.com/~hrbrmstr/cruxjars.git")
# or
devtools::install_git("https://gitlab.com/hrbrmstr/cruxjars.git")
# or (if you must)
devtools::install_github("hrbrmstr/cruxjars")
```

## Usage

```{r lib-ex}
library(cruxjars)

# current version
packageVersion("cruxjars")

```

## cruxjars Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
